Structuring College Access

### 2025-07-03 index.qmd
update maps

      # Example special case for "los_angeles"
      if (m == "los_angeles") {
        rq1_map <- 'https://rq1-map-los-angeles.netlify.app'
      }

>>>>

      # For maps too big to push to GitHub
      if (!m %in% c("atlanta", "boston", "orange_county", "philadelphia", "san_diego")) {
        rq1_map <- paste0('https://rq1-map-', str_replace_all(m, '_', '-'), '.netlify.app')
      }
